Optimizing Large Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2012-01-04 paper/self_calibration_I.tex
euclid: start adding HW comments
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@20088 03a3cea6-2c03-0410-ac9b-9271b1c66c29

\begin{abstract}
In this paper we show that, with a well chosen observing strategy, it is possible to accurately calibrate instruments used in large-scale imaging surveys with survey science data alone. We create end-to-end simulations of an imaging survey, which produces simulated datasets from mock observations of a synthetic sky according to a defined survey strategy. These catalog based simulations include realistic measurement uncertainties and a complex, position-dependent instrument response. We then use a self-calibration technique to recover the relative instrument response by fitting an model that best explains the survey dataset, based on the multiple observations of (non-varying) sources at different focal plane positions. By considering four simple survey strategies we find that, with appropriate redundancy built into the survey strategy, it is possible to accurately constrain the relative photometric response of an imaging instrument, and therefore the relative calibration of all the images and the relative fluxes of all the sources observed. The majority of the remaining post-self-calibration errors are due to the limitations in the basis used to model the relative instrument response. We find that returning the same sources to very different focal plane positions is the key property of any survey strategy designed for accurate calibration. The results of this work suggest the following advice for those considering the design of large scale imaging surveys: Do not use a regular tiling of the sky; instead return the same sources to very different focal plane positions.
\end{abstract}

>>>>

\begin{abstract}
In this paper we show that, with a well chosen observing strategy, it is possible to accurately calibrate the large-scale response of imaging instruments used in large-scale imaging surveys with survey science data alone. We create end-to-end simulations of an imaging survey, which produce simulated photometric catalogs from mock observations of a synthetic sky according to a defined survey strategy. These catalog-based simulations include realistic measurement uncertainties and a complex, position-dependent instrument response. We then use a self-calibration technique to recover the relative instrument response by fitting an model that best explains the survey dataset, based on the multiple observations of (non-varying) sources at different focal plane positions. By considering four simple survey strategies we find that, with appropriate redundancy built into the survey strategy, it is possible to accurately constrain the relative photometric response of an imaging instrument, and therefore the relative calibration of all the images and the relative fluxes of all the sources observed. The majority of the remaining post-self-calibration errors are due to the limitations in the basis used to model the relative instrument response. We find that returning the same sources to very different focal plane positions is the key property of any survey strategy designed for accurate calibration. The results of this work suggest the following advice for those considering the design of large scale imaging surveys: Do not use a regular tiling of the sky; instead return the same sources to very different focal plane positions.
\end{abstract}
